RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2014-11-21 manuscripts/manuscript.Rmd
clarify which function 'automatically adds metadata'

Reading phylogenies from TreeBASE into R was already possible using
the R package `treebase` [@Boettiger_2012]. However, because it relied
on the NEXUS parser provided in the `ape` package, and because of
incompatible flavors of the NEXUS standard [@Vos_2012], 
a sizable number of TreeBASE NEXUS
files could not be read in this way <!-- CB to rephrase to make a -->
<!-- broader point and refer back to arguments made in the NeXML -->
<!-- paper, possibly moving this larger point to the introduction -->.  Owing to the syntactically strict
definition of the
NeXML standard, the RNeXML package can successfully read every 
NeXML document from TreeBASE.

@@

`RNeXML` automatically adds basic metadata by default
<!-- what does "by default" mean here? It doesn't seem like calling -->
<!-- any RNeXML function will add such metadata if it's not there -->
<!-- already? HL -->
<!-- Indeed it does.  We add the time stamp, default license, and user ID even though
     it's not "there" in the data.  -->
such as a time-stamp
of when a tree was produced, and an open data license. The latter by
default is the Creative Commons Zero (CC0) public domain waiver, which
is compatible
with deposition in the Dryad data repository, but can be configured
as a different license if needed.

To adjust these and other metadata fields commonly recommended to be
included with publicly archived data, `RNeXML` provides the `add_basic_meta()`
function.  This function hides the complexities of anchoring metadata
attribute names in common vocabularies from the user.  The
`add_basic_meta()` function takes as input an existing `nexml` object
(like the other `add_` functions, if none is provided it will create one), and at the time
of this writing any of the following
parameters: `title`, `description`, `creator`, `pubdate`, `rights`, `publisher`,
`citation`.  Other metadata elements and corresponding parameters may
be added in the future.

>>>>

@@

`RNeXML`'s `nexml_write` function adds certain basic metadata by automatically
if it has not yet been provided; using default values
consistent with recommended best practices [@Cranston_2014]. At this time,
this includes naming the software generating the NeXML, a time-stamp of
when a tree was produced, and an open data license.

To adjust these values and also add other metadata fields commonly recommended for
includion with publicly archived data, `RNeXML` provides the `add_basic_meta()`
function.  This function hides the complexities of anchoring metadata
attribute names in common vocabularies from the user.  The
`add_basic_meta()` function takes as input an existing `nexml` object
(like the other `add_` functions, if none is provided it will create one), and at the time
of this writing any of the following
parameters: `title`, `description`, `creator`, `pubdate`, `rights`, `publisher`,
`citation`.  Other metadata elements and corresponding parameters may
be added in the future.
